---
title: "p8105_hw1"
output: html_document
date: "2024-09-13"
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

```{r}
data("penguins", package = "palmerpenguins")
```


The dataset contains 344 observations of 3 penguin species on 3 different islands. Aside from the species and island name, the dataset records bill length and depth (in mm), flipper length (in mm), body mass (in gr), sex, and year of observation, totalling in 8 columns and 6 variables. 

The number of rows and columns, respectively, are
```{r echo = FALSE}
nrow(penguins)
ncol(penguins)
```

The mean flipper length, in mm, is `rmean(flipper_length_mm)`
```{r mean}
mean(penguins$flipper_length_mm)
#can't recognize column "flipper_length_mm"
```

**Scatterplot** 
```{r scatterplot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point ()
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
